Workplan

### 2018-04-26 LiteratureReview/LiteratureReview.tex
reorganised workplan and added more to literature review

\title{Literature Review}
\date{2018-04-22}
\author{Jomar Alcantara}

@@

\subsection{Alzheimer's Disease}
\subsection{Vascular Dementia}
\subsection{Dementia with Lewy Bodies}
\subsection{Parkinson's disease dementia}
\subsection{Fronto-temporal dementia}
\subsection{Mild Cognitive Impairment}

@@

\section{Current ways of diagnosing Dementia using Language}

Mini Mental State Examination (MMSE)
Addenbrooke's Cognitive Examination (ACE-III)
Dementia Rating Scale (DRS)
Western Aphasia Battery (WAB)
Boston Diagnostic Aphasia Examination (BDAE)
Boston Naming Test (BNT)

\section{Existing studies that have used Natural Language Processing to help in diagnosing psychological difficulties}

Psychology - Schitzophrenia

\section{What progress has been made in this area already?}

>>>>

\title{Literature Review}
\date{2018-04-26}
\author{Jomar Alcantara}

@@

\subsection{Alzheimer's Disease}
\subsection{Vascular Dementia}
\subsection{Dementia with Lewy Bodies}
\subsection{Parkinson's disease dementia}
\subsection{Fronto-temporal dementia}
\subsection{Primary Progressive Aphasia}
\subsection{Mild Cognitive Impairment}

@@

\section{Current ways of diagnosing Dementia using Language}
Battery of tests to differentiate between Controls, those with MCI, those with AD. 
\begin{itemize}
	\item FCSRDT - As most effective 
	\item Mini Mental State Examination (MMSE)
	\item Addenbrooke's Cognitive Examination (ACE-III)
	\item Dementia Rating Scale (DRS)
	\item Western Aphasia Battery (WAB)
	\item Boston Diagnostic Aphasia Examination (BDAE)
	\item Boston Naming Test (BNT)
\end{itemize}

\section{Existing studies that have used Natural Language Processing to help in diagnosing psychological difficulties, particularly language difficulties}

\subsection{Nun Study - Snowdon (1996)}
\subsection{Comparing Presidents Speeches - Berisha et al (2015)}

### 2018-04-26 Workplan/Workplan.tex
updated structure on Literature Review
reorganised workplan and added more to literature review

	\section{Training needs analysis}
	\subsection{Psychology}
	Training in delivering the WAIS or psychological tools that might be needed 
	\subsection{Programming}
	\begin{itemize}
		\item Online courses in Python Programming
		\item Online courses in Machine Learning
	\end{itemize}

	\subsection{Natural Language Processing}
	Online courses in Natural Language Processing

	\subsection{Signal Processing}
	MATLAB? Speech processing?

	\section{Data collection}
	\subsection{DementiaBank and AphasiaBank}
	Application to be submitted.

@@

	\subsection{Experimental Design}
	Battery of tests to differentiate between Controls, those with MCI, those with AD. 
	\begin{itemize}
		\item FCSRDT - As most effective 
	\end{itemize}

>>>>

	\section{Stages of research}
	\section{Stage 1 - Data capture}
	\subsection{Training needs analysis}
	\subsection{Psychology}
	Training in delivering the WAIS or psychological tools that might be needed 
	\subsection{Programming}
	\begin{itemize}
		\item Online courses in Python Programming
		\item Online courses in Machine Learning
	\end{itemize}

	\section{Data collection}
	\subsection{DementiaBank and AphasiaBank}
	\textbf{Holland Corpus}
	\newline 
	Consists of 2 participants a 62 year old man with mild AD and a 78 year old woman with more advanced AD.
	\newline
	\textbf{Kempler Corpus}
	\newline
	Consists of 6 participants with a range of 65 to 86 (mean, sd)
	\newline
	\textbf{Pitt Corpus}
	\newline
	Consists of 104 control participants, 208 with dementia and 85 with an unknown diagnosis.
	\newline
	\textbf{DePaul Corpus}
	\newline
	Consists of 1 participant, 66 year old female with PPA.
	\newline
	\textbf{Hopkins Corpus}
	\newline
	Consists of 36 participants, 23 males and 13 females

@@

	\section{Stage 2 - Data Processing, Feature Construction}
	\subsection{Natural Language Processing}
	Online courses in Natural Language Processing

	\section{Stage 3 - Data Analysis and Machine Learning}
	\subsection{Application of Machine Learning Algorithms}
